\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-26 paper.tex
BATE-V1

(2) $\mathsf{BATE}$ achieves a good tradeoff between efficiency and optimality. 
Compared with the optimal solutions, (i) our admission control algorithm can speed up the admission procedure by 30$\times$ at the expense of less than 4\% false rejections, 
(ii) our pruning-augmented scheduling algorithm runs $10^2 \sim 10^4 \times$ faster while wasting only 6\% total bandwidth, 
and (iii) our greedy failure recovery algorithm can reduce the reaction time by xx$\times$, 
where profit loss is only around 10\%.

@@

\subsection{Testbed evaluation}\label{testbed-evaluation}
\textbf{Testbed setup}
We build a testbed with 6 servers to emulate a small inter-DC WAN connecting 6 DCs, as shown in Figure \ref{testbed}. 
The inter-DC links run at 1Gbps, and we add 100ms delay on each link to emulate a WAN environment.
Each server is equipped with 4 Intel Xeon E5-2620 CPUs, 64GB memory and 4 Ethernet NICs, 
and on each server we start 20 VMs, which are all connected to an Open vSwitch \cite{openvswitch}.
The VMs run CentOS 7 and use Linux v4.15.6 kernel \cite{Kermel} with our rate limiting module plugged in. 
%We start 21 VMs (1 vCPU, 2GB memory, 100GB disk) in each server, where 20 VMs are used to emulate the hosts and 1 VM runs as the broker.
Every second, we emulate link failures by shutting down the corresponding network interfaces 
under the failure probabilities shown in Fig. \ref{testbed}, 
and bring them online after 3 seconds. 
We also deploy our controller and brokers on extra VMs. 
The network agent module in each broker uses Floodlight \cite{floodlight} to control the vSwitch, 
while the latter monitors link status and reports any failure to the former.
If not stated otherwise, we use 4 shortest paths between each source-destination pair as the tunnels in TE algorithms.

>>>>

(2) $\mathsf{BATE}$ achieves a good tradeoff between efficiency and optimality. 
Compared with the optimal solutions, (i) our admission control algorithm can speed up the admission procedure by 30$\times$ at the expense of less than 4\% false rejections, 
(ii) our pruning-augmented scheduling algorithm runs $10^2 \sim 10^4 \times$ faster while wasting only 6\% total bandwidth, 
and (iii) our greedy failure recovery algorithm can reduce the reaction time by at least 90\%, 
where profit loss is only around 10\%.

@@

\subsection{Testbed evaluation}\label{testbed-evaluation}
\textbf{Testbed setup.}
We build a testbed with 6 servers to emulate a small inter-DC WAN connecting 6 DCs, as shown in Figure \ref{testbed}. 
The inter-DC links run at 1Gbps, and we add 100ms delay on each link to emulate a WAN environment.
Each server is equipped with 4 Intel Xeon E5-2620 CPUs, 64GB memory and 4 Ethernet NICs, 
and on each server we start 20 VMs, which are all connected to an Open vSwitch \cite{openvswitch}.
The VMs run CentOS 7 and use Linux v4.15.6 kernel \cite{Kermel} with our rate limiting module plugged in. 
%We start 21 VMs (1 vCPU, 2GB memory, 100GB disk) in each server, where 20 VMs are used to emulate the hosts and 1 VM runs as the broker.
Every second, we emulate link failures by shutting down the corresponding network interfaces 
under the failure probabilities shown in Fig. \ref{testbed}, 
and bring them online after 3 seconds. 
We also deploy our controller and brokers on extra VMs. 
The network agent module in each broker uses Floodlight \cite{floodlight} to control the vSwitch, 
while the latter monitors link status and reports any failure to the former.
If not stated otherwise, we use 4-shortest paths between each source-destination pair as the tunnels in TE algorithms.
